### 2022-04-20 ms/ms.rmd
re-writing MS:

To understand changes in physiological rates we often look to comparing $Q_{10}$ values, which describe the multiplicative change in physiological rates across a 10&deg;C temperature change. Higher $Q_{10}$ values indicate stronger changes in physiological rates, and it is expected that acclimation should reduce $Q_{10}$ values [@Seebacher2015]. Currently, however, we do not have effect sizes and associated sampling variances derived for $Q_{10}$ making it challenging to weight effect size estimates by sampling variance as is typical in meta-analysis. While the Delta method can be used to approximate the sampling variance (e.g., see Havird *et. al.* @Havird2020) this assumes  $Q_{10}$ is normally distributed and linear with respect to temperature. Unfortunately, this is not the case for $Q_{10}$, as such, the Delta method is likely a poor approximation to sampling variance. There are easier ways to derive effect sizes and associated samping variance for $Q_{10}$ given that $Q_{10}$ is simply a reformulation of a very commonly used effect size in the meta-analysis literature, the log response ratio (*lnRR*) [@hedges1999meta; @laj2011]. Recognition of the similarity between *lnRR* and $Q_{10}$ means we can derive $Q_{10}$ based effect sizes using the well known mathematical properties of *lnRR*, while also providing easy ways to extend this to effect sizes that compare variances in physiological rates [@nakagawa2015meta] and improve upon our ability to account for sources of non-independence that are typical in meta-analysis [@laj2011; @Noble2017]. As such, here we derive a series of $Q_{10}$ based effect sizes along with their associated sampling variances that allow one to compare both changes in mean and variance of physiological rates.

>>>>

Following @Noble2022 we calculated a series of temperature corrected effect sizes that compared mean physiological rates ($lnRR_{Q_{10}}$) as well as the variability in physiological rates ($lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$). These effect sizes are essentially similar to the traditional $Q_{10}$,
